---
title: "Assignment_4"
author: "Matthew Smith"
format: html
editor: visual
output-file: "index.html"
---

## Problem 1A:

```{r}
#| warning: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(reactable)
library(plotly)
library(crosstalk)
df<-read.csv("https://manctsui.github.io/datasets/timesData.csv")
#knitr::kable(head(df, 10))

###Problem 1A###

Top_Three <- df |>
  count(country) |>
  arrange(desc(n)) |>
  slice_head(n=3)
  
reactable(Top_Three,
    columns = list(
      country = colDef(name = "Country"), 
      n = colDef(name = "Number of Universities in Ranking")
      )
    )
```

## Problem 1B:

```{r}
plot_ly(Top_Three, 
        x=~country, 
        y=~n, 
        type = "bar") %>%
  layout(title = "Top Three Countries", 
         xaxis = list(title = "Country"), 
         yaxis = list(title = "Number of Universities")
         )
```

## Problem 2A

```{r}
Top_50 <-df |>
  filter(year == 2011) |>
  mutate(world_rank = as.numeric(world_rank)) |>
  select(world_rank,university_name) |>
  slice_head(n = 50)

reactable(Top_50,
          columns = list(
          university_name = colDef(name = "University Name"), 
          world_rank = colDef(name = "Global Ranking")
      )
    )
```

## Problem 2B

If were were to take the data frame from problem 1A, rank would not be a good choice for a key. In problem 1A there are only two columns, "country" and "Number of Universities in Ranking", so rank isn't even a column to consider. Additionaly, even if rank were in this data frame it would not make a good key because there are ties in the ranking. A good key has unique values in each row.

## Problem 2C

```{r}
sd <- SharedData$new(Top_50, key = ~university_name)

filter_slider("rank","Global Rank",sd,~world_rank)
reactable(sd,
          columns = list(
          university_name = colDef(name = "University Name"), 
          world_rank = colDef(name = "Global Ranking")
      )
)
```

## Problem 3

```{r}
p3 <- df |>
  filter(year == 2016) |>
  drop_na(num_students) |>
  mutate(num_students = as.numeric(gsub(",", "", num_students))) |>
  select(student_staff_ratio, num_students, teaching)

sp3 <- SharedData$new(p3)
plot_1<-plot_ly(sp3, 
        x=~num_students, 
        y=~student_staff_ratio, 
        type = "scatter",
        mode = "markers") %>%
  layout(title = "Number of Students vs. Student-Staff Ratio", 
         xaxis = list(title = "Number of Students"), 
         yaxis = list(title = "Student-Staff Ratio")
         )

plot_2<-plot_ly(sp3, 
        x=~student_staff_ratio, 
        y=~teaching, 
        type = "scatter",
        mode = "markers") %>%
  layout(title = "Student-Staff Ratio vs. Teaching Score", 
         xaxis = list(title = "Student-Staff Ratio"), 
         yaxis = list(title = "Teaching Score")
         )

bscols(
  plot_1,
  plot_2
)
```
